%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{pifont}
\usepackage{marvosym}
\usepackage{wasysym}
\begin{document}

\header{Simon}{Hollingshead}{BA Hons. (Cantab.)} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------
\begin{aside} % In the aside, each new line forces a line break
\section{contact}
22 Polsloe Road
Exeter, Devon
EX1 2HL
~
\href{mailto:me@simonhollingshead.com}{\footnotesize{me@simonhollingshead.com}}
~
07580 619 346
01483 \textbf{[ASK ME]}
~
{\textbf{Recruiter?  Contact by:}}
Email, InMail, Mobile \ding{51}
Work Phone \ding{55}
~
Latest CV always at:
\href{http://cv.simonhollingshead.com/}{\footnotesize{cv.simonhollingshead.com}}
\section{languages}
English (Native)
Japanese (Beginner)
\section{tech skills}
\textbf{Strong}
Java
Hadoop MapReduce
SQL
Python
PHP, CSS, HTML5, JS
SML, Prolog
~
\textbf{Practicing}
C++
Puppet
Vagrant
\section{interests}
Automation (DevOps)
Big Data/Visualisations
{\footnotesize Natural Language Processing}
Security Conferences
CTF Competitions
~
Behavioural Economics
PC Building
Scavenger Hunts
Sushi
Walking
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2011--2014}
{BA Hons. {\normalfont in Computer Science (Class }2.1{\normalfont )}}
{Queens' College, University of Cambridge}
{In this three year course, I was exposed to over fifty different lecture series covering everything from the lowest level hardware to the highest level programming languages and E-commerce concepts.

~

}
%------------------------------------------------
\entry
{2009--2011}
{A Levels {\normalfont (}A* {\normalfont Computing, }A* {\normalfont Maths, }A {\normalfont Fthr. Maths, }A {\normalfont Physics)}}
{Exeter College, Exeter}
{}
%------------------------------------------------
\entry
{2005--2009}
{GCSEs {\normalfont (11 }A* {\normalfont -- }A{\normalfont ) and} FSMQ {\normalfont (}B {\normalfont in Additional Maths)}}
{St James' School, Exeter}
{
~

A full academic history is provided at \href{http://cv.simonhollingshead.com/grades.html}{http://cv.simonhollingshead.com/}.
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
\entry
{{\footnotesize Since Sep 2014}}
{BAE Systems Applied Intelligence, Guildford}
{}
{\emph{Delivery Graduate}, Commercial Solutions Managed Security \\
Since joining, I have learned to use Hadoop MapReduce and Hive to analyse terabytes of network data for anomalous activity.  Within the engineering team, I have developed using Flume, Kafka and ElasticSearch for new service lines, and I continue to assist in increasing efficiency in the Security Operations Centre through creating useful utilities and informative visualisations.

~

}
%------------------------------------------------
\entry
{2010}
{St James' School, Exeter}
{}
{\emph{Additional Mathematics Teacher} \\
After completing the FSMQ course in 2009, I returned to St James' School the following year to teach the new students the more complex parts of the course that the teachers were less familiar with. These classes helped me to find out how to plan, explain, and show people how to do things they have never done before.

~

}
%------------------------------------------------
\entry
{2009 -- 2011}
{GlobalGamingHQ}
{}
{\emph{Site Development Manager} \\
GlobalGamingHQ has run many websites and forums, but their most popular is RuneHQ, a RuneScape fansite with hundreds of thousands of hits per month, meaning developing fast loading pages, intuitive layouts and responding to community feedback was incredibly important and gave me a great `jumping in at the deep end' introduction to large-scale web development and management.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{training}

\begin{entrylist}
%------------------------------------------------
\entry
{Jan 2015}
{HDP Developer: Java {\normalfont by QA for HortonWorks}}
{London}
{This four-day course trains participants on advanced methods of using Hadoop and MapReduce alongside other utilities such as Oozie, HBase, Pig and Hive.}
%------------------------------------------------
\end{entrylist}
\end{document}

